Appendix 1: sdmTMB statistical model description

### 2021-12-22 doc/appendix-model.Rmd
Edit

---
title: "Appendix 1: sdmTMB statistical model description"
output:
  bookdown::pdf_document2:
    toc: true
    number_sections: false
fig_caption: true
urlcolor: blue
highlight: "monochrome"
csl: mee.csl
bibliography: refs.bib
header-includes:
  \usepackage[left]{lineno}
  \usepackage{bm}
  \usepackage{amssymb}
---

@@

where $\gamma_t$ is an example optional time-varying regression parameter and $x_{\s,t}$ is the corresponding predictor value.
This is defined via the `time_varying` argument, assuming that the `time` argument is also supplied a column name.
For example, `time_varying ~ 0 + x`.
The first value is given an implicit uniform prior. 
I.e., the same variable should not appear in the fixed effect formula since the initial value is estimated as part of the time-varying formula.
The formula `time_varying = ~ 1` implicitly represents a time-varying intercept and the intercept should be omitted from the main effects (`~ + 0` or `~ -1`).

>>>>

---
title: "Appendix 1: sdmTMB statistical model description"
output:
  bookdown::pdf_document2:
    toc: true
    number_sections: true
fig_caption: true
urlcolor: blue
highlight: "monochrome"
csl: mee.csl
bibliography: refs.bib
header-includes:
  \usepackage[left]{lineno}
  \usepackage{bm}
  \usepackage{amssymb}
---

@@

where $\gamma_t$ is an example optional time-varying regression parameter and $x_{\s,t}$ is the corresponding predictor value.
This is defined via the `time_varying` argument, assuming that the `time` argument is also supplied a column name.
For example, `time_varying ~ 0 + x`.
The first value is given an implicit uniform prior. 
I.e., the same variable should not appear in the fixed effect formula since the initial value is estimated as part of the time-varying formula.
The formula `time_varying = ~ 1` implicitly represents a time-varying intercept and, this case, the intercept should be omitted from the main effects (`formula ~ + 0 + ...` or `formula ~ -1 + ...`).
